---
title: "Presentation-Basic R Operations"
subtitle: "Create dataframe & Select & Filter & Mutate"  
author: 
  - "Peng Zhang"
date: 'October 1, 2022'
output:
  xaringan::moon_reader:
    css: xaringan-themer.css
    nature:
      slideNumberFormat: "%current%"
      highlightStyle: github
      highlightLines: true
      ratio: 16:9
      countIncrementalSlides: true
---

```{r setup, include=FALSE}
options(htmltools.dir.version = FALSE)
knitr::opts_chunk$set(
  fig.width=9, fig.height=3.5, fig.retina=3,
  out.width = "100%",
  cache = FALSE,
  echo = TRUE,
  message = FALSE, 
  warning = FALSE,
  hiline = TRUE
)
```

```{r xaringan-themer, include=FALSE, warning=FALSE}
library(xaringanthemer)
style_duo_accent(
  primary_color = "#1381B0",
  secondary_color = "#FF961C",
  inverse_header_color = "#FFFFFF"
)
```

## Introduction

This presentation is to demonstrate how to create a dataframe in **R** and perform a few simple operations.


### Create a new dataframe

We can create a dataframe from the below code:
```{r create_df}
df <- data.frame(name = c('John', 'Ty', 'Jim'),
                 age = c(21, 30, 45),
                 title = c('Estimator', 'Engineer', 'Manager'))
df
```


---
name: 

### Operations on dataframe

We can select a particular column and output the specified column only.
```{r select}
# load necessary library
library(tidyverse)

df_1 <- df |> select(title)
df_1
```


---
name: 

### Operations on dataframe

We can filter the dataframe based on a certain condition. 
In the following example, it will only output people with their age over 30.

```{r filter}
df_2 <- df |> filter(age >30)
df_2
```



---
name: 

### Operations on dataframe

We can also add a new column in the dataframe. 
In the following example, we have added division information.

```{r mutate}
df_3 <- df |> mutate(division = c('I', 'II', 'III'))
df_3
```



---
class: center, middle

## Last Advise: Practice, Practice, and Practice ...
# Thanks!

Slides created for MDS DSCI 521 Course Lab4
